Market simulator

### 2020-09-28 analysis/05_market_simulator.Rmd
Added fileInputs. Not connected to anything yet.

# Initial persona configuration
persona_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
)
```

>>>>

# Initial persona configuration
persona_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
)

# Organization file input
fileInput(
  "file_org",
  "Import Organization Data"
)

# Persona file input
fileInput(
  "file_per",
  "Import Persona Data"
)
```
